Manuscript_Github_Pchabaudi_pir_TPMHeatmaps

### 2021-04-22 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_pir_TPMHeatmaps.Rmd
02h time point was missinggit status

combined_data_pir <- combined_data_pir[,c(ordering(colnames(combined_data_pir)[-1], 
                                                   order_vector)),
                                       drop = FALSE]

@@

#Add a column for the subfam (ref for the reference genes)
combined_data_pir_ht$subfam <- ifelse(rownames(combined_data_pir_ht) %in% cir_id,
                                      cir_info$subfam[match(rownames(combined_data_pir_ht), 
                                                            cir_info$Geneid)],
                                      'ref')

@@

anc_ha <- rowAnnotation(foo = anno_mark(at =  na.omit(match(clade_info, 'ancestral')) , 
                                        labels = 'ancestral',
                                        labels_gp = gpar(fontsize = 7),
                                        link_width = unit(3, "mm")))

@@

ht <- Heatmap(
  log2(1+combined_data_pir_ht[,!colnames(combined_data_pir_ht) %in% 'chapl_aapl_name']),
  cluster_rows = FALSE,
  cluster_columns = FALSE,
  show_row_names = FALSE,
  name = 'log(TPM+1)', 
  col = colorRamp2(c(0,
                     maxcol/4,
                     maxcol/2,
                     3*maxcol/4,
                     maxcol),
                   viridis(5)),
  na_col = 'white', 
  border = TRUE,
  border_gp = gpar(lwd = 0.1),
  column_names_gp = gpar(fontsize = 10),
  row_dend_width = unit(3, "cm"),
  width = unit(4.5, 'cm'),
  height = unit(7,'cm'),
  # row_title = NULL,
  row_title_rot = 0,
  row_title_gp = gpar(fontsize = 10),
  row_split = 
    factor(combined_data_pir_ht$chapl_aapl_name,
              levels = ordering(combined_data_pir_ht$chapl_aapl_name,
                                order_vector = 'ChAPL')),
  heatmap_legend_param = list(
    labels_gp = gpar(fontsize = 10),
    title_gp = gpar(fontsize = 10,
                    fontface = 'bold'),
    at = c(0,
           maxcol/4,
           maxcol/2,
           3*maxcol/4,
           maxcol)
  ),
  row_gap = unit(c(rep.int(1, times = 2),
                   3,
                   rep.int(1, times = 4)), "mm")
)

>>>>

@@

#Add a column for the subfam (ref for the reference genes)
combined_data_pir_ht$subfam <- ifelse(rownames(combined_data_pir_ht) %in% cir_id,
                                      cir_info$subfam_num[match(rownames(combined_data_pir_ht), 
                                                            cir_info$Geneid)],
                                      'ref')

@@

# anc_ha <- rowAnnotation(foo = anno_mark(at =  na.omit(match(clade_info, 'ancestral')) , 
#                                         labels = 'ancestral',
#                                         labels_gp = gpar(fontsize = 7),
#                                         link_width = unit(3, "mm")))

@@

ht <- Heatmap(
  log2(1+combined_data_pir_ht[,!colnames(combined_data_pir_ht) %in% 'chapl_aapl_name']),
  cluster_rows = FALSE,
  cluster_columns = FALSE,
  show_row_names = FALSE,
  name = 'log(TPM+1)', 
  col = colorRamp2(c(0,
                     maxcol/4,
                     maxcol/2,
                     3*maxcol/4,
                     maxcol),
                   viridis(5)),
  na_col = 'white', 
  border = TRUE,
  border_gp = gpar(lwd = 0.1),
  column_names_gp = gpar(fontsize = 10),
  row_dend_width = unit(3, "cm"),
  width = unit(4.5, 'cm'),
  height = unit(7,'cm'),
  # row_title = NULL,
  row_title_rot = 0,
  row_title_gp = gpar(fontsize = 7),
  row_split = 
    factor(combined_data_pir_ht$chapl_aapl_name,
              levels = ordering(combined_data_pir_ht$chapl_aapl_name,
                                order_vector = 'ChAPL')),
  heatmap_legend_param = list(
    labels_gp = gpar(fontsize = 10),
    title_gp = gpar(fontsize = 10,
                    fontface = 'bold'),
    at = c(0,
           maxcol/4,
           maxcol/2,
           3*maxcol/4,
           maxcol)
  ),
  row_gap = unit(c(rep.int(1, times = 2),
                   3,
                   rep.int(1, times = 4)), "mm")
)
